DSSynth: An Automated Digital Controller Synthesis Tool for Physical Plants

### 2017-08-16 ase2017/paper.tex
nudge

The proposed synthesis methodology for closed-loop digital control
systems is based on the DSSynth tool~\cite{abate2017, abatecav2017}, 
which can be split into two main stages as follows: manual and 
automated steps, as illustrated in Fig.~\ref{fig:synthesis-flow}. 
%
\begin{figure}[ht!]
\centering
\includegraphics[width=0.45\textwidth]{synthesis-flow.pdf}
\caption{Digital Controller Synthesis Methodology.}
\label{fig:synthesis-flow}
\end{figure}

@@

Our CEGIS engine is implemented as an integrated module within the C bounded
model checker (CBMC)~\cite{cbmc}.  CBMC transforms the ANSI-C representation
of our closed-loop control system model into its internal format.  We
instrument this IR for each synthesis or verification scenario accordingly,
and use CBMC as an oracle to answer our queries.  CBMC itself relies on an
underlying SAT or SMT solver to solve verification conditions.  We~model FWL
effects, time discretization and the presence of quantization noise
explicitly using CBMC's nondeterminism API (e.g., \texttt{nondet},
\texttt{CPROVER\_assume} intrinsic functions).  Our module is included in
CBMC~5.7 and is available for
download.\footnote{\url{https://github.com/diffblue/cbmc/archive/cbmc-5.7.zip}}
We further created a VirtualBox OVA image with our tool pre-installed,
including our MATLAB-generated benchmarks and benchmark shell script with
instructions to run all benchmarks and reproduce our
experiments.\footnote{\url{www.cprover.org/DSSynth/controller-synthesis-cav-2017.tar.gz}}
The current development branch of our toolbox is available in a public
GitHub
repository.\footnote{\url{https://github.com/ssvlab/dsverifier/tree/master/toolbox-dssynth}}

>>>>

The proposed synthesis methodology for closed-loop digital control
systems is based on the DSSynth tool~\cite{abate2017, abatecav2017}, 
which can be split into two main stages as follows: manual and 
automated steps, as illustrated in Fig.~\ref{fig:synthesis-flow}.

\begin{figure}[ht!]
\centering
\includegraphics[width=0.47\textwidth]{synthesis-flow.pdf}
\caption{Phases of the Controller Synthesis}
\label{fig:synthesis-flow}
\end{figure}

@@

Our CEGIS engine is implemented as an integrated module within the C bounded
model checker (CBMC)~\cite{cbmc}.  CBMC transforms the ANSI-C representation
of our closed-loop control system model into its internal format.  We
instrument this IR for each synthesis or verification scenario accordingly,
and use CBMC as an oracle to answer our queries.  CBMC itself relies on an
underlying SAT or SMT solver to solve verification conditions.  We~model FWL
effects, time discretization and the presence of quantization noise
explicitly using CBMC's nondeterminism API (e.g., \texttt{nondet},
\texttt{CPROVER\_assume} intrinsic functions).  Our module is included in
CBMC~5.7 and is available for
download.\footnote{\url{https://github.com/diffblue/cbmc/archive/cbmc-5.7.zip}}
We further created a VirtualBox OVA image with our tool pre-installed,
including our MATLAB-generated benchmarks and benchmark shell script with
instructions to run all benchmarks and reproduce our
experiments.\footnote{\url{www.cprover.org/DSSynth/controller-synthesis-cav-2017.tar.gz}}
Our toolbox is available
online.\footnote{\url{https://github.com/ssvlab/dsverifier/tree/master/toolbox-dssynth}}
